The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-29 paper/paper.tex
paper: improvements to comparison table

\begin{tabularx}{\linewidth}{lYcYYl}
  \toprule
  arity                     & formalisation style          & iteration                       & relevance                     & logical structure    \\
  \midrule
  \multirow{6}{1cm}{unary}  & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & predicate            \\
                            &                              &                                 & relevant                      & family               \\
                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}                                     \\
                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & subobject            \\
                            &                              &                                 & relevant                      & fibration            \\
                            &                              & \multicolumn{2}{l}{iterated}    & augmented semi-simplicial set                        \\
  \midrule
  \multirow{6}{1cm}{binary} & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & relation             \\
                            &                              &                                 & relevant                      & correspondence       \\
                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}                                     \\
                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & fibered relation ?   \\
                            &                              &                                 & relevant                      & span               & \\
                            &                              & \multicolumn{2}{l}{iterated}    & semi-cubical set                                     \\
  \bottomrule
\end{tabularx}

In a previous paper~\citep{hr25}, we exploited this correspondence to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity. That is, instead of the following illustration of the semi-cubical case (upto faces identities),

\begin{equation*}
  \begin{tikzcd}
    X_0: \U & X_1: \U \arrow[l, "\partial^L" description, shift left=2] \arrow[l, "\partial^R" description, shift right=2] & X_2: \U \arrow[l, "\partial^{L\kstar}" description, shift left=6] \arrow[l, "\partial^{R\kstar}" description, shift left=2] \arrow[l, "\partial^{\kstar L}" description, shift right=2] \arrow[l, "\partial^{\kstar R}" description, shift right=6] & \ldots
  \end{tikzcd}
\end{equation*}
we consider a family of relevant relations as shown below:
\begin{equation*}
  \begin{array}{lll}
    E_0 & :               \U                                                                          \\
    E_1 & :               E_0 \times X_0 \rightarrow  \U                                              \\
    E_2 & : \Pi a b c d.\,  E_1(a,b) \times E_1 (c,d) \times E_1(a,c) \times E_1 (b,d) \rightarrow \U \\
    \ldots
  \end{array}
\end{equation*}

@@

>>>>

\begin{tabularx}{\linewidth}{cYcYYl}
  \toprule
  arity                       & formalisation style        & iteration                       & relevance        & logical structure               \\
  \midrule
  \multirow{6}{0.6cm}{unary}  & \multirow{3}{1cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & predicate                       \\
                              &                            &                                 & relevant         & family                          \\
                              &                            & iterated                        & relevant         & \emph{this work}                \\
                              & \multirow{3}{1cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & subobject                       \\
                              &                            &                                 & relevant         & fibration                       \\
                              &                            & iterated                        & relevant         & augmented semi-simplicial set   \\
  \midrule
  \multirow{6}{0.6cm}{binary} & \multirow{3}{1cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & relation                        \\
                              &                            &                                 & relevant         & correspondence                  \\
                              &                            & iterated                        & relevant         & \emph{this work}                \\
                              & \multirow{3}{1cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & fibered relation ?              \\
                              &                            &                                 & relevant         & span                          & \\
                              &                            & iterated                        & relevant         & semi-cubical set                \\
  \bottomrule
\end{tabularx}

In~\citep{hr25}, this correspondence was exploited to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity. That is, instead of the following illustration of the semi-cubical case (upto faces identities),

\begin{equation*}
  \begin{tikzcd}
    X_0: \U & X_1: \U \arrow[l, "\partial^L" description, shift left=2] \arrow[l, "\partial^R" description, shift right=2] & X_2: \U \arrow[l, "\partial^{L\kstar}" description, shift left=6] \arrow[l, "\partial^{R\kstar}" description, shift left=2] \arrow[l, "\partial^{\kstar L}" description, shift right=2] \arrow[l, "\partial^{\kstar R}" description, shift right=6] & \ldots
  \end{tikzcd}
\end{equation*}
a family of relevant relations was considered, as shown below:
\begin{equation*}
  \begin{array}{lll}
    E_0 & :               \U                                                                          \\
    E_1 & :               E_0 \times X_0 \rightarrow  \U                                              \\
    E_2 & : \Pi a b c d.\,  E_1(a,b) \times E_1 (c,d) \times E_1(a,c) \times E_1 (b,d) \rightarrow \U \\
    \ldots
  \end{array}
\end{equation*}

@@

For $\nu$ an arity, that is $1$ in the case of predicates, families and augmented semi-simplicial sets or $2$ in the case of relations, correspondences and semi-cubical sets, such sequence of was called a $\nu$-set.
Equations specifying such sequence of relevant relations were given in \cite{hr25}. Because of the dependency of $E_{n+1}$ into all $E_p$ for $p \leq n$, the family could not be expressed as a function. Instead, it was expressed as a stream whose $(n+1)$-th element $E_{n+1}$ was dependent on the bundle of all previous elements of the stream.
